An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-06-20 reports/manuscript.tex
Unlink table 1 and RoB
Also had to rename all the supp materials

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5394}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} The Centre for Social Impact, University of New South Wales, Sydney, Australia\\\textsuperscript{8} The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland}

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this review, we harmonised 255 effects representing unique combinations of exposures and outcomes from 103 meta-analyses (2,496 primary studies; 2,026,054 participants).
Some types of screen use, such as social media, were consistently correlated with risks to health.
However, other forms of screen use showed associations with benefits.
For example, experimental evidence showed that video games improve aspects of cognitive function.
Some types of screen use have complex associations with outcomes.
For example, general screen use (i.e., content not indicated) showed correlations with harm for body composition, depression, and learning.
However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
}

@@

The most frequently reported exposures were physically active video games (\emph{n} = 31), general screen use (\emph{n} = 27), general TV programs and movies (\emph{n} = 20), and screen-based interventions to promote health (\emph{n} = 14).
Supplementary File 5 provides a list of all exposures identified.
The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 25), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
Full characteristics of the included studies are provided in Table 1.
After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.
These effects represent the findings of 2,496 primary studies, involving 2,026,054 participants.
The characteristics of the included effects are available in Supplementary File 9.

@@

There were 89 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
We removed 28 effects that did not provide individual study-level data, 19 effects with samples \textless{} 1,000, and 19 effects with a significant Egger's test or insufficient studies to conduct the test.
Effects not meeting one or more of these standards are presented in Supplementary File 6.
The remaining 23 effects met our criteria for statistical credibility and are described in Figure 2.
These 23 effects came from 18 meta-analytic reviews analysing data from 338 empirical studies with 262,537 individual participants.

@@

We identified 165 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
We removed 41 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
No remaining studies showed evidence of excessive significance.
Effects not meeting one or more of these standards are presented in Supplementary File 7.
The remaining 21 meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
These 21 effects came from 15 meta-analytic reviews analysing data from 344 empirical studies with 859,562 individual participants.

Digital advertising of unhealthy foods---both traditional advertising and video games developed by a brand for promotion---were associated with higher unhealthy food intake.
Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
General screen use was positively associated with depression, with stronger associations observed for adolescents than other groups.
Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for younger children.
All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
Screen-based interventions which target health behaviours appeared mostly effective.

Across the health outcomes, most (14 of 21) effects were statistically significant at the 99.9\% confidence interval level, with the remaining four significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
Additionally, most effects were small, with the association between screen use and sleep duration the largest at \(r = -0.37\) (\(k = 10, N = 56,720\)).
Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).

@@

As an example, consider children watching television programs---an often cited form of screen use harm.
We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{28}
Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
Similar nuanced findings were observed for video games.
The credible evidence we identified showed that video game playing was associated with poorer body composition and learning.\textsuperscript{27,29}
However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{30}
One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 6 \& 7) therefore this hypothesis could not be addressed.

@@

Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Materials).
For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.\textsuperscript{36}
Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups.\textsuperscript{37}
Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
However, in the absence of this work, our study has shown how children are affected by screens in general.

@@

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{46}).
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
However, we provide the complete results in the supplementary material, along with the dataset for others to consider alternative criteria.

@@

To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{50,51}
Effect sizes on the original metric are provided in Supplementary File 2.
Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
These are similar to other interpretations based on empirical data.\textsuperscript{53}

@@

Direction of Effect:
Finally, we examined the extent to which significance testing suggested screen exposure was associated with benefit, harm, or no effect on outcomes.
We used thresholds of \(P < .05\) for weak evidence and \(P < 10^{-3}\) for strong evidence.
An effect with statistical credibility but with \(P > .05\) was taken to indicate no association of interest.

@@

\leavevmode\hypertarget{ref-R-metafor}{}%
54. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2022).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={An umbrella review of the benefits and risks associated with youths' interactions with electronic screens},
  pdfauthor={Taren Sanders*1, Michael Noetel2, Philip Parker1, Borja Del Pozo Cruz3, 14, 15, Stuart Biddle4, 13, Rimante Ronto5, Ryan Hulteen6, Rhiannon Parker7, George Thomas8, Katrien De Cocker9, Jo Salmon10, Kylie Hesketh10, Nicole Weeks1, Hugh Arnott1, Emma Devine11, Roberta Vasconcellos1, Rebecca Pagano12, Jamie Sherson12, James Conigrave1, \& Chris Lonsdale1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5405}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\title{An umbrella review of the benefits and risks associated with youths' interactions with electronic screens}
\author{Taren Sanders*\textsuperscript{1}, Michael Noetel\textsuperscript{2}, Philip Parker\textsuperscript{1}, Borja Del Pozo Cruz\textsuperscript{3, 14, 15}, Stuart Biddle\textsuperscript{4, 13}, Rimante Ronto\textsuperscript{5}, Ryan Hulteen\textsuperscript{6}, Rhiannon Parker\textsuperscript{7}, George Thomas\textsuperscript{8}, Katrien De Cocker\textsuperscript{9}, Jo Salmon\textsuperscript{10}, Kylie Hesketh\textsuperscript{10}, Nicole Weeks\textsuperscript{1}, Hugh Arnott\textsuperscript{1}, Emma Devine\textsuperscript{11}, Roberta Vasconcellos\textsuperscript{1}, Rebecca Pagano\textsuperscript{12}, Jamie Sherson\textsuperscript{12}, James Conigrave\textsuperscript{1}, \& Chris Lonsdale\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{2} School of Psychology, University of Queensland, Brisbane, Australia\\\textsuperscript{3} Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark\\\textsuperscript{4} Centre for Health Research, University of Southern Queensland, Springfield, Australia\\\textsuperscript{5} Department of Health Sciences, Faculty of Medicine, Health and Human Sciences, Macquarie University, Macquarie Park, Australia\\\textsuperscript{6} School of Kinesiology, Louisiana State University, Baton Rouge, USA\\\textsuperscript{7} The Centre for Social Impact, University of New South Wales, Sydney, Australia\\\textsuperscript{8} The University of Queensland, Health and Wellbeing Centre for Research Innovation, School of Human Movement and Nutrition Sciences, Brisbane, Australia\\\textsuperscript{9} Department of Movement and Sport Science, Ghent University, Ghent, Belgium\\\textsuperscript{10} Institute for Physical Activity and Nutrition, Deakin University, Geelong, Australia\\\textsuperscript{11} The Matilda Centre for Research in Mental Health and Substance Use, University of Sydney, Sydney, Australia\\\textsuperscript{12} School of Education, Australian Catholic University, North Sydney, Australia\\\textsuperscript{13} Faculty of Sport \& Health Sciences, University of Jyväskylä, Finland\\\textsuperscript{14} Department of Physical Education, Faculty of Education, University of Cádiz, Cádiz, Spain\\\textsuperscript{15} Biomedical Research and Innovation Institute of Cádiz (INiBICA) Research Unit, Puerta del Mar University Hospital, University of Cádiz, Cádiz, Spain}

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this review, we harmonised 255 effects representing unique combinations of exposures and outcomes from 103 meta-analyses (2,496 primary studies; 2,026,054 participants).
Some types of screen use, such as social media, were consistently correlated with risks to health.
However, other forms of screen use showed associations with benefits.
For example, educational screen use was generally associted with better learning outcomes.
Some types of screen use have complex associations with outcomes.
For example, television viewing showed harmful correlations with body composition and learning.
However, when parents watched with their children or the content was educational, general screen use was associated with greater learning.
More nuanced guidelines are needed to help parents, teachers, and practitioners ensure that youth benefit from their interactions with screens.
}

@@

The most frequently reported exposures were physically active video games (\emph{n} = 31), general screen use (\emph{n} = 27), general TV programs and movies (\emph{n} = 20), and screen-based interventions to promote health (\emph{n} = 14).
Supplementary File 1 provides a list of all exposures identified.
The most frequently reported outcomes were body composition (\emph{n} = 30), general learning (\emph{n} = 25), depression (\emph{n} = 13), and general literacy (\emph{n} = 12).
Of the 274 unique exposure/outcome combinations, 242 occurred in only one review, with 23 appearing twice, and 9 appearing three or more times.
Full characteristics of the included studies are provided in Supplementary File 2.
After removing reviews with duplicate exposure/outcome combinations, our process yielded 255 unique effect/outcome combinations (retaining multiple effects for different age groups or study designs) contributed from 103 reviews.
These effects represent the findings of 2,496 primary studies, involving 2,026,054 participants.
The characteristics of the included effects are available in Supplementary File 3.

@@

There were 89 unique effects associated with education outcomes, including general learning outcomes, literacy, numeracy, and science.
We removed 28 effects that did not provide individual study-level data, 19 effects with samples \textless{} 1,000, and 19 effects with a significant Egger's test or insufficient studies to conduct the test.
Effects not meeting one or more of these standards are presented in Supplementary File 4.
The remaining 23 effects met our criteria for statistical credibility and are described in Figure 2.
These 23 effects came from 18 meta-analytic reviews analysing data from 338 empirical studies with 262,537 individual participants.

@@

We identified 165 unique outcome-exposure combinations associated with health or health-related behaviour outcomes.
We removed 41 effects that did not provide individual study-level data, 50 effects with samples \textless{} 1,000, and 53 effects with a significant Egger's test or insufficient studies to conduct the test.
No remaining studies showed evidence of excessive significance.
Effects not meeting one or more of these standards are presented in Supplementary File 5.
The remaining 21 meta-analytic associations met our criteria for credible evidence and are described below (see also Figure 3).
These 21 effects came from 15 meta-analytic reviews analysing data from 344 empirical studies with 859,562 individual participants.

Digital advertising of unhealthy foods---both traditional advertising and video games developed by a brand for promotion---were associated with higher unhealthy food intake.
Social media use and sexual content were positively associated with risky behaviors (e.g., sexual activity, risk taking, and substance abuse).
Television viewing was negatively correlated with sleep duration, but with stronger evidence only observed for adolescents.
All forms of screen use (general, television, and video games) were associated with body composition (e.g., higher BMI).
Screen-based interventions which target health behaviours appeared mostly effective.

Across the health outcomes, most (14 of 21) effects were statistically significant at the 99.9\% confidence interval level, with the remaining four significant at 95\% confidence.
However, most of the credible effects exhibited high levels of heterogeneity, with all but two having \(I^2 > 75\%\).
Additionally, most effects were small, with the association between internet use and depression the largest at \(r = 0.25\) (\(k = 118, N = 527,696\)).
Most of the effect sizes (17/21) had an absolute value of \(r < 0.2\).

@@

As an example, consider children watching television programs---an often cited form of screen use harm.
We found statistically robust evidence for a small association with poorer academic performance and literacy skills for general television watching\textsuperscript{27}.
However, we also found evidence that if the content of the program was educational, or the child was watching the program with a parent (i.e., co-viewing), this exposure was instead associated with better literacy.\textsuperscript{28}
Thus, parents may play an important role in selecting content that is likely to benefit their children or, perhaps, interact with their children in ways that may foster literacy (e.g., asking their children questions about the program).
Similar nuanced findings were observed for video games.
The credible evidence we identified showed that video game playing was associated with poorer body composition and learning.\textsuperscript{27,29}
However, when the video game were designed specifically to teach numeracy, playing these games showed learning benefits.\textsuperscript{30}
One might expect that video games designed to be physically active could confer health benefits, but none of the meta-analyses examining this hypothesis met our thresholds for statistical credibility (see Supplementary Files 4 \& 5) therefore this hypothesis could not be addressed.

@@

Largely owing to a small number of studies or missing individual study data, there were few age-based conclusions that could be drawn from reviews which met our criteria for statistical certainty.
If we expand to include those reviews which did not meet this threshold, there remained no clear pattern although there were some age-specific differences in associations (data available in Supplementary Files 4 \& 5).
For example, advertising of unhealthy food was associated with unhealthy food choice for young children, but was not statistically significant for other age groups.\textsuperscript{36}
Conversely, TV programs and movies were more strongly associated with lower physical activity for adolescents than for younger age groups.\textsuperscript{37}
Given the differences in development across childhood and adolescence and the different ways children of various ages use screens, further examination of age-based differences is needed.
However, in the absence of this work, our study has shown how children are affected by screens in general.

@@

Our high-level approach limits the feasibility of examining fine-grained details of the individual studies.
For example, we did not examine moderators beyond age, nor did we rate the risk of bias for the individual studies.
Thus, our assessment of evidence quality was restricted to statistical credibility, rather than a more complete assessment of quality (e.g., GRADE\textsuperscript{46}).
As such, we made decisions regarding the credibility of evidence, where others may have used different thresholds or metrics.
In addition, when faced with duplicate outcome/exposure combinations we chose to keep the one with the largest pooled sample size, assuming that this would capture the most comprehensive and most recent review.
Inspection of the excluded effect sizes suggests that this decision was not that impactful: our results would have been almost exactly the same has we used the number of included studies (\emph{k}) or the most recent review by publication year.
However, we provide the complete results in Supplementary Files 4 \& 5, along with the dataset (Supplementary File 6) for others to consider alternative criteria.

@@

To facilitate comparisons, we converted effect sizes to Pearson's \(r\) using established formulae.\textsuperscript{50,51}
Effect sizes on the original metric are provided in Supplementary File 6.
Throughout the results section we interpret the size of the effects using Funder and Ozer's guidelines:\textsuperscript{52} very small (0.05 \textless{} r \textless= 0.1), small (0.1 \textless{} r \textless= 0.2), medium (0.2 \textless{} r \textless= 0.2), large (0.3 \textless{} r \textless= 0.4), and very large (r \textgreater= 0.4).
These are similar to other interpretations based on empirical data.\textsuperscript{53}

@@

Direction of Effect:
Finally, we examined the extent to which significance testing suggested screen exposure was associated with benefit, harm, or no effect on outcomes.
We used thresholds of \(P < .05\) for weak evidence (i.e., 95\% confidence intervals did not cross zero) and \(P < 10^{-3}\) (i.e., 99.9\% confidence intervals did not cross zero) for strong evidence.
An effect with statistical credibility but with \(P > .05\) (i.e., 95\% confidence intervals included zero) was taken to indicate no association of interest.

@@

\leavevmode\hypertarget{ref-R-metafor}{}%
54. Viechtbauer, W. \emph{Metafor: Meta-analysis package for r}. (2023).
